Attack-Tolerance in Structured Networks via Multipath Routing \\ Draft: 2016-02-21

### 2016-02-21 ec-2016/source/paper.tex
Add rest of routing overview.

\newcommand{\beq}{\begin{eqnarray}}
\newcommand{\eeq}{\end{eqnarray}}
\DeclareMathOperator{\wbf}{wBF}

@@

% Title portion
\title{
Attack-Tolerance in Structured Networks via Multipath Routing
\\ Draft: 2016-02-18
}
\author{EDWARD L. PLATT
\affil{University of Michigan}
DANIEL M. ROMERO
\affil{University of Michigan}}

@@

>>>>

\usepackage{tikz}
\usetikzlibrary{chains,decorations.pathreplacing}
\newcommand{\beq}{\begin{eqnarray}}
\newcommand{\eeq}{\end{eqnarray}}
\DeclareMathOperator{\wbf}{wBF}

@@

% Title portion
\title{
Attack-Tolerance in Structured Networks via Multipath Routing
\\ Draft: 2016-02-21
}
\author{EDWARD L. PLATT
\affil{University of Michigan}
DANIEL M. ROMERO
\affil{University of Michigan}}

@@

More specifically, the algorithm can be understood by dividing the bits of
$z$ into four segments: $A, B, C, D$ (Figure \ref{fig:route-overview}).
$A$ is the first $h$ bits, followed by $B$ until reaching $C$: the last $h$ bits before
the destination level $l_w$, and then finally $D$.
As the routing algorithm progresses through the levels $l$, the segments of $z$
get updated in order.
Because of vertex transitivity, we can make the simplifying assumption
that $v = (0,0)$ without loss of generality.
Initially (1) while still in the source trusted neighborhood,
$A$ is set to match $s$, which ensures that no two
paths will share nodes outside the trusted neighborhood.
Then (2) the bits of $B$ are inverted and (3) a cyclic permutation of $s$ is
placed into $C$.
After this step (4--6), $D$, $A$, and $B$ are set to their destination values.
After $A$ is set, the path remains distinct from other paths because other nodes
either have uninverted values in $B$ or a different value of $\tilde{s}$ in $C$.
While (7) $C$ is being set to the destination value, overlaps may occur, but
nodes are now within the trusted neighborhood of the destination.

\begin{figure}
\begin{center}
\begin{tikzpicture}[
node distance=0pt,
 start chain = A going right,
    X/.style = {rectangle, draw,% styles of nodes in string (chain)
                minimum width=10ex, minimum height=3ex,
                outer sep=0pt, on chain},
    B/.style = {decorate,
                decoration={brace, amplitude=5pt,
                pre=moveto,pre length=1pt,post=moveto,post length=1pt,
                raise=1mm,
                            #1}, % for mirroring of brace, if necessary
                thick},
    B/.default=mirror, % by default braces are mirrored
                        ]
\foreach \i in {0\ldots,{\ldots}0\ldots,{\ldots}0\ldots,{\ldots}0}% <-- content of nodes
    \node[X] {\i};
\draw[B] ( A-1.north west) -- node[above=1.5mm] {$h$} ( A-1.north east);
\draw[B] ( A-2.north west) -- node[above=1.5mm] {$l_w - 2h$} ( A-2.north east);
\draw[B] ( A-3.north west) -- node[above=1.5mm] {$h$} ( A-3.north east);
\draw[B] ( A-4.north west) -- node[above=1.5mm] {$m - l_w$} ( A-4.north east);
\draw ( A-1.west) -- node[left=5ex,minimum width=10ex] {start} ( A-1.west);
\node (B1) [inner sep=1pt,above=of A-1.north,above=5ex] {\underline{A}};
\node (B2) [inner sep=1pt,above=of A-2.north,above=5ex] {\underline{B}};
\node (B3) [inner sep=1pt,above=of A-3.north,above=5ex] {\underline{C}};
\node (B4) [inner sep=1pt,above=of A-4.north,above=5ex] {\underline{D}};
\end{tikzpicture}
\\
\begin{tikzpicture}[
node distance=0pt,
 start chain = A going right,
    X/.style = {rectangle, draw,% styles of nodes in string (chain)
                minimum width=10ex, minimum height=3ex,
                outer sep=0pt, on chain},
                        ]
\foreach \i in {$s$,{\ldots}0\ldots,{\ldots}0\ldots,{\ldots}0}% <-- content of nodes
    \node[X] {\i};
\draw ( A-1.west) -- node[left=5ex,minimum width=10ex] {1.} ( A-1.west);
\end{tikzpicture}
\\
\begin{tikzpicture}[
node distance=0pt,
 start chain = A going right,
    X/.style = {rectangle, draw,% styles of nodes in string (chain)
                minimum width=10ex, minimum height=3ex,
                outer sep=0pt, on chain},
                        ]
\foreach \i in {$s$,{\ldots}1\ldots,{\ldots}0\ldots,{\ldots}0}% <-- content of nodes
    \node[X] {\i};
\draw ( A-1.west) -- node[left=5ex,minimum width=10ex] {2.} ( A-1.west);
\end{tikzpicture}
\\
\begin{tikzpicture}[
node distance=0pt,
 start chain = A going right,
    X/.style = {rectangle, draw,% styles of nodes in string (chain)
                minimum width=10ex, minimum height=3ex,
                outer sep=0pt, on chain},
                        ]
\foreach \i in {$s$,{\ldots}1\ldots,{\ldots}$\tilde{s}$\ldots,{\ldots}0}% <-- content of nodes
    \node[X] {\i};
\draw ( A-1.west) -- node[left=5ex,minimum width=10ex] {3.} ( A-1.west);
\end{tikzpicture}
\\
\begin{tikzpicture}[
node distance=0pt,
 start chain = A going right,
    X/.style = {anchor=base, rectangle, draw,% styles of nodes in string (chain)
                minimum width=10ex, minimum height=3ex,
                outer sep=0pt, on chain},
                        ]
\foreach \i in {$s$,{\ldots}1\ldots,{\ldots}$\tilde{s}$\ldots,$z_{w,D}$}% <-- content of nodes
    \node[X] {\i};
\draw ( A-1.west) -- node[left=5ex,minimum width=10ex] {4.} ( A-1.west);
\end{tikzpicture}
\\
\begin{tikzpicture}[
node distance=0pt,
 start chain = A going right,
    X/.style = {anchor=base, rectangle, draw,% styles of nodes in string (chain)
                minimum width=10ex, minimum height=3ex,
                outer sep=0pt, on chain},
                        ]
\foreach \i in {$z_{w,A}$,{\ldots}1\ldots,{\ldots}$\tilde{s}$\ldots,$z_{w,D}$}% <-- content of nodes
    \node[X] {\i};
\draw ( A-1.west) -- node[left=5ex,minimum width=10ex] {5.} ( A-1.west);
\end{tikzpicture}
\\
\begin{tikzpicture}[
node distance=0pt,
 start chain = A going right,
    X/.style = {anchor=base, rectangle, draw,% styles of nodes in string (chain)
                minimum width=10ex, minimum height=3ex,
                outer sep=0pt, on chain},
                        ]
\foreach \i in {$z_{w,A}$,$z_{w,B}$,{\ldots}$\tilde{s}$\ldots,$z_{w,D}$}% <-- content of nodes
    \node[X] {\i};
\draw ( A-1.west) -- node[left=5ex,minimum width=10ex] {6.} ( A-1.west);
\end{tikzpicture}
\\
\begin{tikzpicture}[
node distance=0pt,
 start chain = A going right,
    X/.style = {anchor=base, rectangle, draw,% styles of nodes in string (chain)
                minimum width=10ex, minimum height=3ex,
                outer sep=0pt, on chain},
                        ]
\foreach \i in {$z_{w,A}$,$z_{w,B}$,$z_{w,C}$,$z_{w,D}$}% <-- content of nodes
    \node[X] {\i};
\draw ( A-1.west) -- node[left=5ex,minimum width=10ex] {7.} ( A-1.west);
\end{tikzpicture}
\end{center}
\caption{
Progression of place-within-level $z$ as the multipath routing algorithm
cycles through the levels of the butterfly network.
}
\label{fig:route-overview}
\end{figure}
